\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-29 OaklandSubmission/intro.tex
formal guarantees

\subsubsection*{Formal guarantees} We prove formal correctness and
security theorems for our compiler. The correctness theorem proves a
forward simulation between the
``ideal'' semantics (the trusted-third party semantics) of a source
program and the ``protocol'' semantics (the distributed \mpc
semantics that relies on circuit evaluation) of the corresponding
compiled program. The simulation
guarantees that for a well-typed source program, the two semantics
successfully terminate
(e.g. there are no array index out-of-bounds errors), and that the
observable outputs in the two semantics are
identical. For
the security theorem, we formally reduce the security
of our compiler to the security of the back-end cryptographic
protocol (by also invoking our correctness theorem). We also prove a formal security theorem for our partitioning
scheme.

>>>>

\subsubsection*{Formal guarantees} We prove formal correctness and
security theorems for our compiler. The correctness theorem relates the
``trusted third party'' semantics of a source
program and the ``protocol'' semantics (the distributed \mpc
semantics that relies on circuit evaluation) of the corresponding
compiled program. The theorem
guarantees that for a well-typed source program, the two semantics
successfully terminate
(e.g. there are no array index out-of-bounds errors), and that the
observable outputs in the two semantics are
identical. For
the security theorem, we formally reduce the security
of our compiler to the security of the  \mpc back-end
 (by also invoking our correctness theorem). We also prove a formal security theorem for our partitioning
scheme.
